\documentclass[12pt]{article}
\usepackage[margin=0.6in,top=1.15in,bottom=0.55in]{geometry}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{../../latex/grader-worksheet}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.25em}
\titleformat{\section}{\large\bfseries\scshape}{}{0pt}{}

\GraderSetup{assignment-id=U1L10LE,template-revision=1}

\begin{document}

\begin{center}
{\LARGE\bfseries Week 10 Lit Example Worksheet}\par\vspace{0.05em}
{\large\scshape Julius Caesar: Proof That Misses the Point}\par\vspace{0.12em}
\rule{0.78\textwidth}{0.5pt}
\end{center}

\textbf{Purpose:} Apply Week 10's method to Brutus and Antony. Decide whether proof matches the exact point at issue.

\textbf{Directions:} Use the Lit Example Reader. Do not retell the plot; diagnose the proof-to-claim match.

\section*{Part 1: Brutus's Point at Issue}

\textbf{Question 1.1}\\[-0.15em]
What exact conclusion does Brutus need to prove to justify Caesar's assassination?

\GraderAnswerBox{Part 1 Q1}{1.85in}

\textbf{Question 1.2}\\[-0.15em]
What nearby claim does Brutus try to prove about Caesar's ambition and Roman freedom?

\GraderAnswerBox{Part 1 Q2}{2.05in}

\newpage

\section*{Part 2: Does Brutus's Proof Match?}

\textbf{Question 2.1}\\[-0.15em]
Explain the gap between proving Caesar was ambitious and proving that Caesar had to be killed.

\GraderAnswerBox{Part 2 Q1}{2.35in}

\textbf{Question 2.2}\\[-0.15em]
How does Brutus's slaves/free-men alternative risk proving a nearby point rather than the full point at issue?

\GraderAnswerBox{Part 2 Q2}{2.35in}

\newpage

\section*{Part 3: Antony's Answer}

\textbf{Question 3.1}\\[-0.15em]
Choose two pieces of Antony's evidence. For each, state what smaller claim it actually supports.

\GraderAnswerBox{Part 3 Q1}{2.45in}

\textbf{Question 3.2}\\[-0.15em]
Does Antony's evidence fully prove that the conspirators were wrong to kill Caesar, or does it mainly answer a narrower charge? Explain.

\GraderAnswerBox{Part 3 Q2}{2.45in}

\newpage

\section*{Part 4: Repair or Narrow}

\textbf{Question 4.1}\\[-0.15em]
Rewrite Brutus's case so the conclusion matches the evidence. Either add the missing evidence required for the stronger conclusion or narrow the conclusion to what his evidence actually proves.

\GraderAnswerBox{Part 4 Q1}{2.45in}

\textbf{Question 4.2}\\[-0.15em]
In one paragraph, explain how Week 10's tool helps a reader respect a powerful speech while still asking whether it proves the right point.

\GraderAnswerBox{Part 4 Q2}{2.45in}

\end{document}
