\documentclass[12pt]{article}
\usepackage[margin=0.6in,top=1.15in,bottom=0.55in]{geometry}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{array}
\usepackage[hidelinks]{hyperref}
\usepackage{../../latex/grader-worksheet}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.2em}
\titleformat{\section}{\large\bfseries\scshape}{}{0pt}{}
\newcommand{\cluebox}[1]{\par\vspace{0.1em}\noindent\fbox{\begin{minipage}{\dimexpr\textwidth-2\fboxsep-2\fboxrule}\vspace{0.22em}#1\vspace{0.22em}\end{minipage}}\par\vspace{0.1em}}

\GraderSetup{assignment-id=U1F4LD,template-revision=2}

\begin{document}
\begin{center}
{\LARGE\bfseries Logic Dungeon IV}\par\vspace{0.04em}
{\large\scshape The Archive of Broken Proofs}\par\vspace{0.08em}
\rule{0.78\textwidth}{0.5pt}\par
\end{center}

\textbf{Purpose:} Use the logic tools from Weeks 10--12 to rebuild a conclusion that fits its evidence and decide what limited action it warrants.

\section*{The Proof Workshop}
The Records Service Corridor carries the company of twenty into the working Archive within the outer approach complex of \textit{Castrum Malae Ratiocinationis}. Reaching the Archive does not mean the company has entered the fortress. Here, clerks once hung records beneath brass plates stating the exact question to be answered. A quake, water damage, hurried salvage, and the crisis-era \textbf{Doctrine of Continuance} preserved many genuine records while breaking their connection to the claims they were meant to support.

Near the outbound stair stand three inherited approach chests:
\begin{itemize}[leftmargin=1.5em,itemsep=0.05em]
\item \textbf{Crowned Gate} --- ceremonial plans and royal entry rolls;
\item \textbf{Twin Arches} --- a structural comparison between a repaired western bridge and the East Water Arch;
\item \textbf{Forty-Seven Returns} --- a clean roll of parties returning through Wagon Gate.
\end{itemize}

The transfer cage can carry the twenty adventurers, essential gear, and only \textbf{one approach chest}. Records may be removed from the inherited chests and repacked into one new \textbf{Composite Dossier} chest at the Collation Table. A \textbf{controlled inspection} sends a small inspection party toward an approach while the full company remains uncommitted at a secured muster point.

\cluebox{\textbf{Archive rule:} State the exact point at issue. Preserve what each record really establishes. Test relevant likenesses and important differences. Judge examples together with missing cases and counterexamples. The goal is the \emph{best-supported limited action}, not certainty.}

\textbf{Tools:} point at issue; irrelevant or nearby proof; partial proof and repair; source case, target case, relevant similarity, disanalogy, overextension; induction, sample quality, missing cases, counterexample, claim size, revised conclusion. Spiral tools may be used when needed.

\newpage
\section*{Part 1: The Great Claim Rail}
Three brass question-plates remain on the rail:

\cluebox{\textbf{Plate A:} Which gate was ceremonially principal?\\
\textbf{Plate B:} Which gate carried the fastest light couriers during the two recorded dry seasons?\\
\textbf{Plate C:} What approach action do the surviving records best support now for this company?}

On the floor lie a royal procession roll, Twin-Arches scale drawings, and the clean Forty-Seven Returns roll. None bears its original cord.

\textbf{Question 1.1}\\[-0.15em]
Which plate states the company's actual point at issue? Explain why the other two questions are nearby but insufficient for the decision the company must make.
\GraderAnswerBox{Part 1 Q1}{1.75in}

\textbf{Question 1.2}\\[-0.15em]
Match each loose record to the question it most directly helps answer. For the Twin-Arches drawings, state what additional information is needed before deciding what they prove. What rule should govern every later entry in the Composite Dossier?
\GraderAnswerBox{Part 1 Q2}{1.75in}

\newpage
\section*{Part 2: The Crowned Gate Dossier}
The oldest chest bears a polished conclusion slip:

\cluebox{\textbf{Cover claim:} ``The Crowned Gate is the proper approach for the company because it was the principal gate of the fortress.''\\[0.15em]
\textbf{Records inside:} plans for royal processions; precedence rules placing Crowned first in ceremonies; entry rolls naming dignitaries admitted there. No current inspection, load report, obstruction report, or company-sized passage record survives in the chest.}

\textbf{Question 2.1}\\[-0.15em]
State the conclusion needing proof, the evidence actually offered, the nearby claim that the evidence supports, and what remains unproved about the company's approach.
\GraderAnswerBox{Part 2 Q1}{1.8in}

\textbf{Question 2.2}\\[-0.15em]
Repair the Crowned entry for the Composite Dossier without discarding its genuine evidence. Write a conclusion no broader than the records. Then state what role, if any, the Crowned records should have in planning the approach and justify it.
\GraderAnswerBox{Part 2 Q2}{1.75in}

\newpage
\section*{Part 3: The Paired Works}
Comparator Ilyan's models place a repaired western bridge beside the East Water Arch near Twin Arches.

\cluebox{\textbf{Surviving likenesses:} equal span; matching arch profile; the same dressed stone; similar water marks. The western bridge remained usable after its repair.\\[0.15em]
\textbf{Recovered center leaf:} the western bridge stands on bedrock and carries downward cart weight. The East Water Arch stands on layered fill, receives reverse water pressure, and was later cut for a drainage channel. Its present repair age is unknown.}

A Continuance summary concludes: ``The East Water Arch will bear the company because it matches the repaired western bridge.''

\textbf{Question 3.1}\\[-0.15em]
Identify the source case, target case, and conclusion. Name the most relevant surviving similarity and two disanalogies that matter to the conclusion.
\GraderAnswerBox{Part 3 Q1}{1.8in}

\textbf{Question 3.2}\\[-0.15em]
Judge the analogy: full proof, limited support, overextension, or decoration. Then repair its expedition use. What may it legitimately tell inspectors to compare, and what may it not authorize?
\GraderAnswerBox{Part 3 Q2}{1.8in}

\newpage
\section*{Part 4: The Forty-Seven Returns}
The cleanest instance roll contains forty-seven successful return slips from Wagon Gate:

\cluebox{Thirty-six slips concern mounted couriers, eight concern foot messengers, and three concern light repair teams. Every dated slip comes from one of two dry seasons. The roll contains no failed attempt, no unknown outcome, and no supplied company larger than six. Its cover reads: ``Wagon Gate is the most reliable approach for every company in every season.''}

\textbf{Question 4.1}\\[-0.15em]
Identify the observations, the general claim, and the size of that claim. Evaluate the sample: what does it represent reasonably well, and which important cases are missing?
\GraderAnswerBox{Part 4 Q1}{1.85in}

\textbf{Question 4.2}\\[-0.15em]
Write a useful revised conclusion supported by this roll alone. Then state what action, if any, this roll warrants at this stage and explain the expedition consequence.
\GraderAnswerBox{Part 4 Q2}{1.7in}

\newpage
\section*{Part 5: The Broken Shelf}
Red cord leads to Enumerator Sera's lower-bay records, omitted from the clean roll:

\cluebox{\textbf{Mixed record:} Fourteen supplied work crews of sixteen to twenty-four attempted Wagon Gate across dry, damp, and wet seasons. Ten completed the approach; two withdrew when runoff crossed the marked threshold; one found the gate gear closed and returned; one outcome is unknown. Nine additional wet-season courier parties produced eight recorded returns and one unknown outcome.\\[0.15em]
\textbf{Red-cord case:} A twenty-two-person crew began after runoff crossed the threshold and had to retreat. The Reviser wrote: ``Not always reliable. Preserve the condition.''}

\textbf{Question 5.1}\\[-0.15em]
How does the mixed record change the sample without turning it into certainty? Explain what the red-cord case does to the cover's universal claim and what useful condition it preserves.
\GraderAnswerBox{Part 5 Q1}{1.8in}

\textbf{Question 5.2}\\[-0.15em]
Use the evidence ladder: observations, pattern, limited claim, overclaim, revised conclusion. Decide what action this evidence now warrants and defend the size of that action.
\GraderAnswerBox{Part 5 Q2}{1.9in}

\newpage
\section*{Part 6: The Collation Table}
The table has channels for the exact question, direct records, comparison leaves, instance rolls, and exceptions. It also holds a narrow-claim seal and a \emph{support incomplete} tag.

\textbf{Question 6.1}\\[-0.15em]
Give each inherited dossier its final evidentiary job in one concise entry: Crowned Gate, Twin Arches, and Forty-Seven Returns with the restored lower-bay records. For each, state what belongs in the Composite Dossier and what conclusion must be refused.
\GraderAnswerBox{Part 6 Q1}{2.25in}

\textbf{Question 6.2}\\[-0.15em]
Draft the Composite Dossier's conclusion. It must answer the point at issue, assign a limited role to all three bodies of evidence, and distinguish a controlled first inspection from guaranteed passage or full-company commitment.
\GraderAnswerBox{Part 6 Q2}{2.25in}

\newpage
\section*{Part 7: The Outbound Transfer Stair}
The jammed transfer cage is cleared. It can carry the company, essential gear, and one chest. The expedition also finds fresh wax crumbs and a lamp cup that is still warm, but no identified visitor or trustworthy testimony.

\textbf{Question 7.1}\\[-0.15em]
State the company's final action and what must travel in the Composite Dossier. Use at least three results from different parts. Specify what the small inspection party does while all twenty remain at the secured muster point. Include one inspection check, one stop or retreat condition, and explain why the choice is best supported rather than guaranteed.
\GraderAnswerBox{Part 7 Q1}{2.3in}

\textbf{Question 7.2}\\[-0.15em]
What can logic establish about the dossier and the warm lamp evidence, and what can it not establish by itself? Name the observation, testimony, or judgment still needed before the twenty adventurers commit to entry.
\GraderAnswerBox{Part 7 Q2}{2.0in}

\end{document}
