\documentclass[12pt]{article}
\usepackage[margin=0.6in,top=0.85in,bottom=0.55in]{geometry}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{lastpage}
\usepackage[hidelinks]{hyperref}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.25em}
\setlength{\headheight}{26pt}
\titleformat{\section}{\large\bfseries\scshape}{}{0pt}{}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[C]{\footnotesize Student Name: \hspace{2.3in} \quad Assignment ID: U1L14LE \quad Page \thepage\ of \pageref{LastPage}}
\renewcommand{\headrulewidth}{0.5pt}

\newcommand{\answerbox}[2]{%
\vspace{0.12em}
\noindent\textbf{#1}\par
\vspace{0.04em}
\noindent\fbox{%
\begin{minipage}[t][#2]{\dimexpr\textwidth-2\fboxsep-2\fboxrule}
\rule{\textwidth}{0pt}
\vspace{#2}
\end{minipage}}
\par\vspace{0.22em}}

\begin{document}

\begin{center}
{\LARGE\bfseries Week 14 Lit Example Worksheet}\par\vspace{0.05em}
{\large\scshape Shakespeare: Discovering Too Late}\par\vspace{0.12em}
\rule{0.78\textwidth}{0.5pt}
\end{center}

\textbf{Purpose:} Apply Week 14's intellectual-tool map to Macbeth and Caesar. Decide what facts, terms, or judgments were missing before action.

\textbf{Directions:} Use the Lit Example Reader. Do not retell the plot; map discovery, proof, and judgment.

\section*{Part 1: Macbeth's Late Discoveries}

\textbf{Question 1.1}\\[-0.15em]
What two facts does Macbeth discover too late in the Act 5 passage?

\answerbox{ANSWER LABEL: Part 1 Q1}{2.0in}

\textbf{Question 1.2}\\[-0.15em]
Which term or phrase did Macbeth judge too quickly, and what meaning did later events reveal?

\answerbox{ANSWER LABEL: Part 1 Q2}{2.15in}

\newpage

\section*{Part 2: Macbeth's Failed Judgment}

\textbf{Question 2.1}\\[-0.15em]
Explain why the apparitions' words were not proof that Macbeth was safe.

\answerbox{ANSWER LABEL: Part 2 Q1}{2.3in}

\textbf{Question 2.2}\\[-0.15em]
Complete a Week 14 tool map for Macbeth: question, needed discovery, clarified term, inference test, and judgment.

\answerbox{ANSWER LABEL: Part 2 Q2}{2.55in}

\newpage

\section*{Part 3: Caesar's Evidence and Interpretation}

\textbf{Question 3.1}\\[-0.15em]
What evidence or testimony does Calpurnia offer, and what interpretation does Decius offer?

\answerbox{ANSWER LABEL: Part 3 Q1}{2.35in}

\textbf{Question 3.2}\\[-0.15em]
What pressure or desire may distort Caesar's judgment when he hears Decius's interpretation?

\answerbox{ANSWER LABEL: Part 3 Q2}{2.4in}

\newpage

\section*{Part 4: Comparing the Tragic Failures}

\textbf{Question 4.1}\\[-0.15em]
Compare Macbeth and Caesar. How does each act before discovery and judgment are complete?

\answerbox{ANSWER LABEL: Part 4 Q1}{2.65in}

\textbf{Question 4.2}\\[-0.15em]
Choose Macbeth or Caesar and write one careful alternative judgment the character should have made before acting.

\answerbox{ANSWER LABEL: Part 4 Q2}{2.55in}

\end{document}
