\documentclass[12pt]{article}
\usepackage[margin=0.6in,top=1.15in,bottom=0.55in]{geometry}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{needspace}
\usepackage[hidelinks]{hyperref}
\usepackage{../../latex/grader-worksheet}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.25em}
\titleformat{\section}{\large\bfseries\scshape}{}{0pt}{}

\GraderSetup{assignment-id=U1L16LL,template-revision=1}

\begin{document}

\begin{center}
{\LARGE\bfseries Week 16 Logic Lab}\par\vspace{0.05em}
{\large\scshape Persuasion Is Not Proof}\par\vspace{0.1em}
\rule{0.78\textwidth}{0.5pt}\par\vspace{0.15em}
\end{center}

\noindent\textbf{Purpose:} Apply Week 16 skills to fresh speeches and posts: separate audience effect from claim, name logos/ethos/pathos, and judge what is proved versus only made persuasive.

\vspace{0.3em}

\section*{Part 1: Claim, Audience, Force}

\textbf{Question 1.1}\\[-0.15em]
A student body president ends a morning announcement: ``If you care about this school, wear blue tomorrow and fill the gym. Champions show up.'' Identify the main claim or desired action, the audience, and the main rhetorical force.

\GraderAnswerBox{Part 1 Q1}{2.15in}

\Needspace{3.2in}
\textbf{Question 1.2}\\[-0.15em]
A parent posts: ``Any teacher who assigns weekend work clearly does not respect family time. Real educators protect childhood.'' Identify the claim under proof and one emotion or character pressure the post uses.

\GraderAnswerBox{Part 1 Q2}{2.15in}

\newpage

\section*{Part 2: Logos, Ethos, Pathos}

\textbf{Question 2.1}\\[-0.15em]
A mayoral candidate says, ``I coached youth soccer here for twelve years. Look at these photos of flooded basements. Vote for the drain bond so no child has to sleep upstairs again.'' Label one logos move, one ethos move, and one pathos move.

\GraderAnswerBox{Part 2 Q1}{2.55in}

\textbf{Question 2.2}\\[-0.15em]
A club recruiter tells freshmen, ``Our last three presidents got into top colleges. Join us if you are serious about your future.'' Which appeal is strongest, and what still needs proof before the conclusion follows?

\GraderAnswerBox{Part 2 Q2}{2.45in}

\newpage

\section*{Part 3: Force Versus Proof}

\textbf{Question 3.1}\\[-0.15em]
A coach's halftime speech makes the team louder and more aggressive. The coach claims the other team is ``soft and scared.'' What may the speech accomplish rhetorically, and what has it not yet proved?

\GraderAnswerBox{Part 3 Q1}{2.55in}

\textbf{Question 3.2}\\[-0.15em]
A flyer argues, ``Our after-school coding club raised average math scores last semester; therefore every student should drop music to take coding.'' Separate a supported smaller claim from the overreaching conclusion.

\GraderAnswerBox{Part 3 Q2}{2.55in}

\newpage

\section*{Part 4: Rhetoric-vs-Proof Map in a Paragraph}

\textbf{Question 4.1}\\[-0.15em]
Read the paragraph. Complete a rhetoric-vs-proof map: main claim, audience/desired response, logos, ethos, pathos, what is proved, what is only suggested, and whether rhetorical force matches, exceeds, or replaces proof.

\vspace{0.2em}

\noindent\fbox{%
\begin{minipage}{\dimexpr\textwidth-2\fboxsep-2\fboxrule}
\vspace{0.35em}
At a town meeting, a speaker holds up a cracked water bottle from last summer's heat wave. ``I grew up on this block. You know my family. While consultants collected fees, kids waited in rooms with no air. Approve the cooling-center budget tonight. Anyone who delays this vote is choosing paperwork over children.'' The audience applauds; several people stand.
\vspace{0.35em}
\end{minipage}
}

\GraderAnswerBox{Part 4 Q1}{3.2in}

\newpage

\section*{Part 5: Review}

\textbf{Question 5.1}\\[-0.15em]
Two neighbors argue whether a fence proposal is ``neighborly.'' One means it blocks an ugly view; the other means it respects shared sight lines and light. Use a prior-week dispute tool: name the contested term and whether the dispute is likely verbal, real, or mixed.

\GraderAnswerBox{Part 5 Q1}{2.2in}

\textbf{Question 5.2}\\[-0.15em]
``We should cancel the field trip because the bus company has clean seats.'' Use a prior-week missing-the-point tool: what claim needed proof, and why the reason fails to meet it?

\GraderAnswerBox{Part 5 Q2}{2.05in}

\end{document}
