\documentclass[12pt]{article}
\usepackage[margin=0.6in,top=0.85in,bottom=0.55in]{geometry}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{lastpage}
\usepackage[hidelinks]{hyperref}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.25em}
\setlength{\headheight}{26pt}
\titleformat{\section}{\large\bfseries\scshape}{}{0pt}{}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[C]{\footnotesize Student Name: \hspace{2.3in} \quad Assignment ID: U1L10LL \quad Page \thepage\ of \pageref{LastPage}}
\renewcommand{\headrulewidth}{0.5pt}

\newcommand{\answerbox}[2]{%
\vspace{0.15em}
\noindent\textbf{#1}\par
\vspace{0.05em}
\noindent\fbox{%
\begin{minipage}[t][#2]{\dimexpr\textwidth-2\fboxsep-2\fboxrule}
\rule{\textwidth}{0pt}
\vspace{#2}
\end{minipage}
}\par
\vspace{0.25em}
}

\begin{document}

\begin{center}
{\LARGE\bfseries Week 10 Logic Lab}\par\vspace{0.05em}
{\large\scshape Irrelevant Proof and Missing the Point}\par\vspace{0.1em}
\rule{0.78\textwidth}{0.5pt}\par\vspace{0.15em}
\end{center}

\noindent\textbf{Purpose:} Apply Week 10 skills to new examples. Do not copy examples from the reading handout.

\vspace{0.3em}

\section*{Part 1: Point at Issue}

\textbf{Question 1.1}\\[-0.15em]
Claim needing proof: ``The senior trip should be moved from Friday to Monday.'' Evidence offered: ``The bus company has friendly drivers.'' State the point at issue and explain why the evidence misses it.

\answerbox{ANSWER LABEL: Part 1 Q1}{2.3in}

\textbf{Question 1.2}\\[-0.15em]
Claim needing proof: ``This article is reliable enough to cite in a research paper.'' Evidence offered: ``The article is short and easy to read.'' What does the evidence actually prove, and what remains unproved?

\answerbox{ANSWER LABEL: Part 1 Q2}{2.3in}

\newpage

\section*{Part 2: Nearby Claim}

\textbf{Question 2.1}\\[-0.15em]
``The city should choose the riverfront plan because everyone agrees the riverfront looks ugly right now.'' Identify the nearby claim that may be proved and the larger conclusion that still needs proof.

\answerbox{ANSWER LABEL: Part 2 Q1}{2.55in}

\textbf{Question 2.2}\\[-0.15em]
``Jordan should be team captain because Jordan scored the most points last season.'' Explain how this may prove a nearby claim but not the whole point at issue.

\answerbox{ANSWER LABEL: Part 2 Q2}{2.45in}

\newpage

\section*{Part 3: Repair the Mismatch}

\textbf{Question 3.1}\\[-0.15em]
Repair this argument by either adding evidence that answers the actual issue or narrowing the conclusion: ``The homework policy is fair because it was announced clearly on the first day.''

\answerbox{ANSWER LABEL: Part 3 Q1}{2.8in}

\newpage

\section*{Part 4: Argument in a Paragraph}

\textbf{Question 4.1}\\[-0.15em]
Read the paragraph. Identify the main conclusion, the evidence actually offered, the nearby point it proves, and the question still unanswered.

\vspace{0.2em}

\noindent\fbox{%
\begin{minipage}{\dimexpr\textwidth-2\fboxsep-2\fboxrule}
\vspace{0.35em}
At the meeting, the principal argued that the school should replace the old library roof before buying new scoreboards. She showed photographs of water stains near the history shelves and a repair estimate from two contractors. A coach replied that sports bring the school together, that the basketball team made the playoffs, and that students cheer louder when the gym looks modern. He concluded that the scoreboard purchase should come first.
\vspace{0.35em}
\end{minipage}
}

\answerbox{ANSWER LABEL: Part 4 Q1}{2.75in}

\newpage

\section*{Part 5: Review}

\textbf{Question 5.1}\\[-0.15em]
``Only fair rules let everyone speak before a vote. This rule lets everyone speak before a vote. Therefore this rule is fair.'' Identify the proposition form or structure being used, then say whether the conclusion follows.

\answerbox{ANSWER LABEL: Part 5 Q1}{2.0in}

\textbf{Question 5.2}\\[-0.15em]
``A true leader never changes her mind. Maya changed her mind after new evidence. Therefore Maya is not a true leader.'' Name the main defect from an earlier week and explain it briefly.

\answerbox{ANSWER LABEL: Part 5 Q2}{2.0in}

\end{document}
