\documentclass[12pt]{article}
\usepackage[margin=0.6in,top=1.15in,bottom=0.55in]{geometry}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{../../latex/grader-worksheet}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.25em}
\titleformat{\section}{\large\bfseries\scshape}{}{0pt}{}

\GraderSetup{assignment-id=U1L13LE,template-revision=1}

\begin{document}

\begin{center}
{\LARGE\bfseries Week 13 Lit Example Worksheet}\par\vspace{0.05em}
{\large\scshape Shakespeare: Testing Testimony}\par\vspace{0.12em}
\rule{0.78\textwidth}{0.5pt}
\end{center}

\textbf{Purpose:} Apply Week 13's credibility map to the witches and Brutus. Decide what each source can and cannot prove.

\textbf{Directions:} Use the Lit Example Reader. Do not retell the plot; judge source credibility.

\section*{Part 1: The Witches' Testimony}

\textbf{Question 1.1}\\[-0.15em]
What claims do the witches make about Macbeth, and which claim is soon corroborated?

\GraderAnswerBox{Part 1 Q1}{2.0in}

\textbf{Question 1.2}\\[-0.15em]
Why does the corroborated claim make the witches tempting sources?

\GraderAnswerBox{Part 1 Q2}{2.05in}

\newpage

\section*{Part 2: Limits on the Witches' Credibility}

\textbf{Question 2.1}\\[-0.15em]
What remains uncorroborated or uncertain after Macbeth receives the Cawdor title?

\GraderAnswerBox{Part 2 Q1}{2.2in}

\textbf{Question 2.2}\\[-0.15em]
Write a careful conclusion about how much Macbeth should trust the witches.

\GraderAnswerBox{Part 2 Q2}{2.3in}

\newpage

\section*{Part 3: Brutus as a Source}

\textbf{Question 3.1}\\[-0.15em]
What central claim does Brutus testify to about Caesar, and what access or competence does Brutus have?

\GraderAnswerBox{Part 3 Q1}{2.35in}

\textbf{Question 3.2}\\[-0.15em]
What bias or pressure may affect Brutus's testimony, and what corroboration would make his claim stronger?

\GraderAnswerBox{Part 3 Q2}{2.55in}

\newpage

\section*{Part 4: Careful Trust Judgment}

\textbf{Question 4.1}\\[-0.15em]
Compare the witches and Brutus as sources. In one paragraph, explain why one accurate detail or one honorable speaker is not enough by itself to settle the whole question.

\GraderAnswerBox{Part 4 Q1}{2.65in}

\textbf{Question 4.2}\\[-0.15em]
Choose one source from the reader and complete a credibility map: claim, source, access, bias, corroboration or conflict, and careful conclusion.

\GraderAnswerBox{Part 4 Q2}{2.55in}

\end{document}
