\documentclass[12pt]{article}
\usepackage[margin=0.6in,top=0.85in,bottom=0.55in]{geometry}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{lastpage}
\usepackage[hidelinks]{hyperref}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.25em}
\setlength{\headheight}{26pt}
\titleformat{\section}{\large\bfseries\scshape}{}{0pt}{}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[C]{\footnotesize Student Name: \hspace{2.3in} \quad Assignment ID: U1L12LE \quad Page \thepage\ of \pageref{LastPage}}
\renewcommand{\headrulewidth}{0.5pt}

\newcommand{\answerbox}[2]{%
\vspace{0.12em}
\noindent\textbf{#1}\par
\vspace{0.04em}
\noindent\fbox{%
\begin{minipage}[t][#2]{\dimexpr\textwidth-2\fboxsep-2\fboxrule}
\rule{\textwidth}{0pt}
\vspace{#2}
\end{minipage}}
\par\vspace{0.22em}}

\begin{document}

\begin{center}
{\LARGE\bfseries Week 12 Lit Example Worksheet}\par\vspace{0.05em}
{\large\scshape Shakespeare: Evidence and Character Claims}\par\vspace{0.12em}
\rule{0.78\textwidth}{0.5pt}
\end{center}

\textbf{Purpose:} Apply Week 12's method to Cassius and Lady Macbeth. Decide how far examples support character claims.

\textbf{Directions:} Use the Lit Example Reader. Do not retell the plot; test the evidence-to-claim match.

\section*{Part 1: Cassius's Examples}

\textbf{Question 1.1}\\[-0.15em]
What two examples does Cassius use to make Caesar seem less impressive?

\answerbox{ANSWER LABEL: Part 1 Q1}{1.95in}

\textbf{Question 1.2}\\[-0.15em]
What limited claim about Caesar do those examples support?

\answerbox{ANSWER LABEL: Part 1 Q2}{2.05in}

\newpage

\section*{Part 2: Cassius's Overclaim}

\textbf{Question 2.1}\\[-0.15em]
What larger claim about Caesar or Rome might Cassius want Brutus to infer from these examples?

\answerbox{ANSWER LABEL: Part 2 Q1}{2.25in}

\textbf{Question 2.2}\\[-0.15em]
Why are Cassius's examples not enough by themselves to prove that larger claim?

\answerbox{ANSWER LABEL: Part 2 Q2}{2.25in}

\newpage

\section*{Part 3: Lady Macbeth's Evidence}

\textbf{Question 3.1}\\[-0.15em]
What general claim does Lady Macbeth make about Macbeth's ambition and nature?

\answerbox{ANSWER LABEL: Part 3 Q1}{2.35in}

\textbf{Question 3.2}\\[-0.15em]
What visible evidence in the passage supports her claim, and what evidence would make the claim stronger?

\answerbox{ANSWER LABEL: Part 3 Q2}{2.55in}

\newpage

\section*{Part 4: Revise the Claims}

\textbf{Question 4.1}\\[-0.15em]
Revise Cassius's argument so the conclusion fits the examples he gives.

\answerbox{ANSWER LABEL: Part 4 Q1}{2.45in}

\textbf{Question 4.2}\\[-0.15em]
In one paragraph, explain how Week 12's evidence ladder helps readers make careful claims about character without ignoring powerful examples.

\answerbox{ANSWER LABEL: Part 4 Q2}{2.45in}

\end{document}
