\documentclass[12pt]{article}
\usepackage[margin=0.6in,top=0.85in,bottom=0.55in]{geometry}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{lastpage}
\usepackage[hidelinks]{hyperref}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.25em}
\setlength{\headheight}{26pt}

\titleformat{\section}{\large\bfseries\scshape}{}{0pt}{}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[C]{%
\footnotesize
Student Name: \hspace{2.3in} \quad Assignment ID: U1L7LL \quad Page \thepage\ of \pageref{LastPage}
}
\renewcommand{\headrulewidth}{0.5pt}
\renewcommand{\footrulewidth}{0pt}

\newcommand{\answerbox}[2]{%
\vspace{0.15em}
\noindent\textbf{#1}\par
\vspace{0.05em}
\noindent\fbox{%
\begin{minipage}[t][#2]{\dimexpr\textwidth-2\fboxsep-2\fboxrule}
\rule{\textwidth}{0pt}
\vspace{#2}
\end{minipage}
}\par
\vspace{0.25em}
}

\begin{document}

\begin{center}
{\LARGE\bfseries Week 7 Logic Lab}\par\vspace{0.05em}
{\large\scshape Fallacy Diagnosis: Appearance Versus Proof}\par\vspace{0.1em}
\rule{0.78\textwidth}{0.5pt}\par\vspace{0.15em}
\end{center}

\noindent\textbf{Purpose:} Apply Week 7 skills to new examples. Do not copy examples from the reading handout.

\vspace{0.3em}

\section*{Part 1: False Claim or Bad Inference}

\textbf{Question 1.1}\\[-0.15em]
``All transfer students skip advisory. Maya is a transfer student. Therefore Maya skips advisory.'' Is the main failure a false claim, a bad inference, or both? Explain briefly.

\answerbox{ANSWER LABEL: Part 1 Q1}{2.15in}

\textbf{Question 1.2}\\[-0.15em]
``Devon spoke against the new phone policy in the forum. Therefore Devon does not care about learning.'' Is the main failure a false claim, a bad inference, or both? Explain briefly.

\answerbox{ANSWER LABEL: Part 1 Q2}{2.15in}

\newpage

\section*{Part 2: Appearance of Proof}

\textbf{Question 2.1}\\[-0.15em]
``Anyone who questions the spirit-week schedule is against school pride. You questioned the schedule. Therefore you are against school pride.'' What gives this argument its appearance of strength, and where does the reasoning fail?

\answerbox{ANSWER LABEL: Part 2 Q1}{2.45in}

\newpage

\section*{Part 3: Fallacy Autopsy}

\textbf{Question 3.1}\\[-0.15em]
Perform a fallacy autopsy on this argument: ``If you were a real teammate, you would vote for overnight training camp. You voted against it. Therefore you are not a real teammate.'' State (1) the conclusion, (2) the apparent proof, (3) the defect, and (4) a repaired or narrowed claim.

\answerbox{ANSWER LABEL: Part 3 Q1}{3.15in}

\newpage

\section*{Part 4: Argument in a Paragraph}

\textbf{Question 4.1}\\[-0.15em]
Read the paragraph. Perform a short fallacy autopsy on the main argument. State the conclusion, the apparent proof, and the defect.

\vspace{0.2em}

\noindent\fbox{%
\begin{minipage}{\dimexpr\textwidth-2\fboxsep-2\fboxrule}
\vspace{0.35em}
The cafeteria was loud during fifth lunch. Then the student council president stood up and said the new dress code must be accepted without debate, because every loyal student already supports it and only troublemakers raise objections. Two students near the door laughed about the soup. A teacher asked people to sit down. The president finished by saying that silence would prove loyalty, so anyone still standing should sit and stop opposing the policy.
\vspace{0.35em}
\end{minipage}
}

\answerbox{ANSWER LABEL: Part 4 Q1}{2.55in}

\newpage

\section*{Part 5: Review}

\textbf{Question 5.1}\\[-0.15em]
``All songbirds are animals that can fly long distances over open water. All albatrosses are songbirds. Therefore all albatrosses are animals that can fly long distances over open water.'' Apply the form test, then name the main problem on the fact test.

\answerbox{ANSWER LABEL: Part 5 Q1}{2.15in}

\textbf{Question 5.2}\\[-0.15em]
``All maples are trees. All oaks are trees. Therefore all oaks are maples.'' Is this argument formally valid? Explain briefly.

\answerbox{ANSWER LABEL: Part 5 Q2}{1.85in}

\end{document}
