\documentclass[12pt]{article}
\usepackage[margin=0.6in,top=1.15in,bottom=0.55in]{geometry}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{../../latex/grader-worksheet}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.25em}
\titleformat{\section}{\large\bfseries\scshape}{}{0pt}{}

\GraderSetup{assignment-id=U1L16LE,template-revision=1}

\begin{document}

\begin{center}
{\LARGE\bfseries Week 16 Lit Example Worksheet}\par\vspace{0.05em}
{\large\scshape Shakespeare: Rhetoric and Proof}\par\vspace{0.12em}
\rule{0.78\textwidth}{0.5pt}
\end{center}

\textbf{Purpose:} Apply Week 16's rhetoric-vs-proof analysis to Antony's funeral speech and Lady Macbeth's persuasion.

\textbf{Directions:} Use the Lit Example Reader. Do not retell the plot; separate audience force from logical proof.

\section*{Part 1: Antony --- Claim and Force}

\textbf{Question 1.1}\\[-0.15em]
What main claim or set of claims does Antony press on the crowd, and what response does he want?

\GraderAnswerBox{Part 1 Q1}{2.05in}

\textbf{Question 1.2}\\[-0.15em]
Identify one ethos move and one pathos move in Antony's speech.

\GraderAnswerBox{Part 1 Q2}{2.1in}

\newpage

\section*{Part 2: Antony --- Proof Test}

\textbf{Question 2.1}\\[-0.15em]
What logos-style evidence does Antony offer against the charge that Caesar was ambitious, and what limited point might that evidence support?

\GraderAnswerBox{Part 2 Q1}{2.35in}

\textbf{Question 2.2}\\[-0.15em]
Does Antony's rhetorical force match, exceed, or replace proof for the stronger conclusions about treason and what Rome should do? Explain.

\GraderAnswerBox{Part 2 Q2}{2.45in}

\newpage

\section*{Part 3: Lady Macbeth --- Pressure}

\textbf{Question 3.1}\\[-0.15em]
What does Lady Macbeth want Macbeth to conclude or do, and which appeals does she use?

\GraderAnswerBox{Part 3 Q1}{2.35in}

\textbf{Question 3.2}\\[-0.15em]
After her speech lands emotionally, what moral or factual burden still remains unproved?

\GraderAnswerBox{Part 3 Q2}{2.5in}

\newpage

\section*{Part 4: Compare and Judge}

\textbf{Question 4.1}\\[-0.15em]
Complete a brief rhetoric-vs-proof map for one passage: claim, audience, key appeals, proved, only suggested, force vs proof.

\GraderAnswerBox{Part 4 Q1}{2.75in}

\textbf{Question 4.2}\\[-0.15em]
Compare the two passages. Why can a speech be powerful without settling the claim that actually needs proof?

\GraderAnswerBox{Part 4 Q2}{2.5in}

\end{document}
