\documentclass[12pt]{article}
\usepackage[margin=0.6in,top=0.85in,bottom=0.55in]{geometry}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{lastpage}
\usepackage{array}
\usepackage[hidelinks]{hyperref}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.25em}
\setlength{\headheight}{26pt}

\titleformat{\section}{\large\bfseries\scshape}{}{0pt}{}
\titleformat{\subsection}{\normalsize\bfseries}{}{0pt}{}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[C]{%
\footnotesize
Student Name: \hspace{2.3in} \quad Assignment ID: U1L1AL \quad Page \thepage\ of \pageref{LastPage}
}
\renewcommand{\headrulewidth}{0.5pt}
\renewcommand{\footrulewidth}{0pt}

\newcommand{\argumentbox}[2]{% #1 = label e.g. "Part 1 Q1 ARGUMENT BOX", #2 = height e.g. 2.6in
\vspace{0.15em}
\noindent\textbf{#1}\par
\vspace{0.05em}
\noindent\fbox{%
\begin{minipage}[t][#2]{\dimexpr\textwidth-2\fboxsep-2\fboxrule}
\rule{\textwidth}{0pt}
\vspace{#2}
\end{minipage}
}\par
\vspace{0.25em}
}

\begin{document}

\begin{center}
{\LARGE\bfseries What Follows From What? Argument Lab}\par\vspace{0.05em}
{\large\scshape Week 1: Whately on Logic and Reasoning}\par\vspace{0.1em}
\rule{0.78\textwidth}{0.5pt}\par\vspace{0.15em}
\end{center}

\noindent\textbf{Purpose:} This lab helps you practice the structure of an argument: the conclusion, the stated reason, the hidden assumption, and the test of whether the conclusion actually follows. Use your marked Whately reading handout while you work. Your answers should focus on reasoning, not just whether you agree with the topic.

\vspace{0.3em}

\section*{Part 1: Model the Four-Step Test}

\textbf{Part 1 Q1:} Read the model argument below. Then explain, in your own words, how the four-step test works. Your answer must be labeled with \textbf{Conclusion}, \textbf{Stated reason}, \textbf{Hidden assumption}, and \textbf{Follows}.

\vspace{0.15em}
\noindent\textbf{Model argument:} ``This rule is popular with most students, so it must be fair.''

\begin{itemize}[leftmargin=*, itemsep=0.08em, topsep=0.08em, parsep=0pt]
\item \textbf{Conclusion:} Put the conclusion here.
\item \textbf{Stated reason:} Put the stated reason here.
\item \textbf{Hidden assumption:} Put the hidden assumption here.
\item \textbf{Follows:} Explain whether the conclusion follows here.
\end{itemize}

\argumentbox{Part 1 Q1 ARGUMENT BOX}{2.25in}

\newpage

\section*{Part 2: Test Fresh Arguments}

\textbf{Part 2 Q1:} Analyze this argument: ``The city placed a bronze statue of this man in the town square, so he must have lived nobly.'' Identify the conclusion, stated reason, hidden assumption, and whether the conclusion follows.

\argumentbox{Part 2 Q1 ARGUMENT BOX}{2.45in}

\textbf{Part 2 Q2:} Analyze this argument: ``The first essay uses more difficult words than the second essay, so the first essay must have better reasoning.'' Identify the conclusion, stated reason, hidden assumption, and whether the conclusion follows.

\argumentbox{Part 2 Q2 ARGUMENT BOX}{2.45in}

\newpage

\textbf{Part 2 Q3:} Analyze this argument: ``Our class has always done the assignment this way, so this way must be the best way to do it.'' Identify the conclusion, stated reason, hidden assumption, and whether the conclusion follows.

\argumentbox{Part 2 Q3 ARGUMENT BOX}{2.45in}

\textbf{Part 2 Q4:} Analyze this argument: ``Every just rule should treat the same action the same way. This rule punishes one student and excuses another student for the same action. Therefore, this rule is not just.'' Identify the conclusion, stated reason, hidden assumption, and whether the conclusion follows.

\argumentbox{Part 2 Q4 ARGUMENT BOX}{2.45in}

\newpage

\section*{Part 3: Literary Anchor}

\textbf{Part 3 Q1:} Choose \textbf{one} of the claims below and analyze it with the four-step test. Your answer must identify the conclusion, stated reason, hidden assumption, and whether the conclusion follows.

\begin{itemize}[leftmargin=*, itemsep=0.08em, topsep=0.08em, parsep=0pt]
\item \textbf{Macbeth claim:} ``The witches predicted Macbeth's future, so Macbeth is not responsible for what he later chooses.''
\item \textbf{Caesar claim:} ``Caesar may become dangerous later, so Brutus is justified in killing him now.''
\end{itemize}

\argumentbox{Part 3 Q1 ARGUMENT BOX}{2.75in}

\section*{Part 4: Repair and Create}

\textbf{Part 4 Q1:} Choose \textbf{one weak argument} from Part 2. Rewrite it so that the conclusion is better supported or more careful. You may change the conclusion, add a missing reason, or narrow the claim.

\argumentbox{Part 4 Q1 ARGUMENT BOX}{1.8in}

\newpage

\textbf{Part 4 Q2:} Write one original argument about a school rule, a speaker in \textit{Macbeth} or \textit{Julius Caesar}, a public speech, a sports decision, or a family disagreement. Then analyze your own argument with the four-step test.

\argumentbox{Part 4 Q2 ARGUMENT BOX}{2.65in}

\section*{Part 5: Exit Claim}

\textbf{Part 5 Q1:} Complete this claim in one strong paragraph: \textbf{Logic helps a reader most when \underline{\hspace{1.25in}} because \underline{\hspace{1.6in}}.} Use one example from Whately, \textit{Macbeth}, or \textit{Julius Caesar}.

\argumentbox{Part 5 Q1 ARGUMENT BOX}{2.35in}

\end{document}
