\documentclass[12pt]{article}
\usepackage[margin=0.6in,top=1.15in,bottom=0.55in]{geometry}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{../../latex/grader-worksheet}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.25em}
\titleformat{\section}{\large\bfseries\scshape}{}{0pt}{}

\GraderSetup{assignment-id=U1L17LE,template-revision=1}

\begin{document}

\begin{center}
{\LARGE\bfseries Week 17 Lit Example Worksheet}\par\vspace{0.05em}
{\large\scshape Shakespeare: Self-Deception}\par\vspace{0.12em}
\rule{0.78\textwidth}{0.5pt}
\end{center}

\textbf{Purpose:} Apply Week 17's self-deception autopsy to Macbeth's private reasoning and Brutus's orchard justification.

\textbf{Directions:} Use the Lit Example Reader. Do not retell the plot; use multiple Whately tools on each speaker's self-justification.

\section*{Part 1: Macbeth --- Desire and Knowledge}

\textbf{Question 1.1}\\[-0.15em]
What desire or feared loss drives Macbeth in the Passage 1 speech, and what conclusion is he testing?

\GraderAnswerBox{Part 1 Q1}{2.05in}

\textbf{Question 1.2}\\[-0.15em]
What reasons against the murder does Macbeth already see, and what spur does he name?

\GraderAnswerBox{Part 1 Q2}{2.1in}

\newpage

\section*{Part 2: Macbeth --- Autopsy}

\textbf{Question 2.1}\\[-0.15em]
Surface a hidden assumption that would be needed to treat the murder as acceptable, and name one Whately tool that exposes later self-deception risk.

\GraderAnswerBox{Part 2 Q1}{2.35in}

\textbf{Question 2.2}\\[-0.15em]
Offer a repaired narrower claim Macbeth could honestly make at this moment without pretending necessity.

\GraderAnswerBox{Part 2 Q2}{2.45in}

\newpage

\section*{Part 3: Brutus --- Private Case}

\textbf{Question 3.1}\\[-0.15em]
What desire for Rome or for his own honor seems to drive Brutus, and what conclusion does he reach?

\GraderAnswerBox{Part 3 Q1}{2.35in}

\textbf{Question 3.2}\\[-0.15em]
What stated reasons and analogy does he use, and what remains unproved?

\GraderAnswerBox{Part 3 Q2}{2.5in}

\newpage

\section*{Part 4: Full Map and Comparison}

\textbf{Question 4.1}\\[-0.15em]
Complete a self-deception autopsy for Brutus: desire, conclusion, stated reasons, hidden assumption, exposing tool, remaining need, repaired claim.

\GraderAnswerBox{Part 4 Q1}{2.75in}

\textbf{Question 4.2}\\[-0.15em]
Compare Macbeth and Brutus. How can private reasoning hide from itself while still using recognizable logical forms?

\GraderAnswerBox{Part 4 Q2}{2.5in}

\end{document}
