\documentclass[12pt]{article}
\usepackage[margin=0.6in,top=1.15in,bottom=0.55in]{geometry}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{../../latex/grader-worksheet}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.25em}
\titleformat{\section}{\large\bfseries\scshape}{}{0pt}{}

\GraderSetup{assignment-id=U1L15LE,template-revision=1}

\begin{document}

\begin{center}
{\LARGE\bfseries Week 15 Lit Example Worksheet}\par\vspace{0.05em}
{\large\scshape Shakespeare: Verbal and Real Disputes}\par\vspace{0.12em}
\rule{0.78\textwidth}{0.5pt}
\end{center}

\textbf{Purpose:} Apply Week 15's dispute map to contested words in Macbeth and Julius Caesar.

\textbf{Directions:} Use the Lit Example Reader. Do not retell the plot; classify the kind of dispute and explain what remains after clarification.

\section*{Part 1: Macbeth and the Word Man}

\textbf{Question 1.1}\\[-0.15em]
What contested term drives the Macbeth passage, and what does Lady Macbeth seem to mean by it?

\GraderAnswerBox{Part 1 Q1}{2.05in}

\textbf{Question 1.2}\\[-0.15em]
What does Macbeth's reply suggest about his meaning of the same term?

\GraderAnswerBox{Part 1 Q2}{2.1in}

\newpage

\section*{Part 2: Classifying Macbeth's Dispute}

\textbf{Question 2.1}\\[-0.15em]
After the contested term is clarified, what real disagreement remains between Macbeth and Lady Macbeth?

\GraderAnswerBox{Part 2 Q1}{2.35in}

\textbf{Question 2.2}\\[-0.15em]
Classify the Macbeth dispute as verbal, real, or mixed. Explain your classification.

\GraderAnswerBox{Part 2 Q2}{2.45in}

\newpage

\section*{Part 3: Caesar and Public Words}

\textbf{Question 3.1}\\[-0.15em]
What claim does Brutus make about Caesar, and what contested term must the crowd understand before judging that claim?

\GraderAnswerBox{Part 3 Q1}{2.35in}

\textbf{Question 3.2}\\[-0.15em]
What examples does Antony offer, and how do they pressure Brutus's use of the contested term?

\GraderAnswerBox{Part 3 Q2}{2.5in}

\newpage

\section*{Part 4: Dispute Map and Comparison}

\textbf{Question 4.1}\\[-0.15em]
Complete a dispute map for the Caesar passage: contested term, Brutus's meaning, Antony's pressure on that meaning, shared claim, remaining disagreement, and classification.

\GraderAnswerBox{Part 4 Q1}{2.75in}

\textbf{Question 4.2}\\[-0.15em]
Compare the two passages. Why does clarifying a powerful word help without automatically settling the whole conflict?

\GraderAnswerBox{Part 4 Q2}{2.5in}

\end{document}
