\documentclass[12pt]{article}
\usepackage[margin=0.6in,top=0.85in,bottom=0.55in]{geometry}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{lastpage}
\usepackage[hidelinks]{hyperref}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.25em}
\setlength{\headheight}{26pt}

\titleformat{\section}{\large\bfseries\scshape}{}{0pt}{}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[C]{%
\footnotesize
Student Name: \hspace{2.3in} \quad Assignment ID: U1L3LL \quad Page \thepage\ of \pageref{LastPage}
}
\renewcommand{\headrulewidth}{0.5pt}
\renewcommand{\footrulewidth}{0pt}

\newcommand{\answerbox}[2]{%
\vspace{0.15em}
\noindent\textbf{#1}\par
\vspace{0.05em}
\noindent\fbox{%
\begin{minipage}[t][#2]{\dimexpr\textwidth-2\fboxsep-2\fboxrule}
\rule{\textwidth}{0pt}
\vspace{#2}
\end{minipage}
}\par
\vspace{0.25em}
}

\begin{document}

\begin{center}
{\LARGE\bfseries Week 3 Logic Lab}\par\vspace{0.05em}
{\large\scshape Propositions and Clear Claims}\par\vspace{0.1em}
\rule{0.78\textwidth}{0.5pt}\par\vspace{0.15em}
\end{center}

\noindent\textbf{Purpose:} Apply Week 3 skills to new examples. Do not copy examples from the reading handout.

\vspace{0.3em}

\section*{Part 1: Propositions and Structure}

\textbf{Question 1.1}\\[-0.15em]
``Please submit the form by Friday.'' Is this a proposition? Explain briefly.

\answerbox{ANSWER LABEL: Part 1 Q1}{1.45in}

\textbf{Question 1.2}\\[-0.15em]
``Some volunteers missed the safety briefing.'' Identify the subject, predicate, quality, and quantity.

\answerbox{ANSWER LABEL: Part 1 Q2}{1.75in}

\newpage

\section*{Part 2: Standard Form (A, E, I, O)}

\textbf{Question 2.1}\\[-0.15em]
``No smartphones in this lab are devices that may be used during the exam.'' Name the standard form (A, E, I, or O), quality, and quantity.

\answerbox{ANSWER LABEL: Part 2 Q1}{1.65in}

\textbf{Question 2.2}\\[-0.15em]
``At least one finalist is a student who speaks three languages.'' Name the standard form (A, E, I, or O), quality, and quantity.

\answerbox{ANSWER LABEL: Part 2 Q2}{1.65in}

\newpage

\section*{Part 3: Translate Ordinary Language}

\textbf{Question 3.1}\\[-0.15em]
``Only employees with a valid badge may enter the server room.'' Translate into a clear standard-form categorical proposition. State the subject and predicate you chose.

\answerbox{ANSWER LABEL: Part 3 Q1}{2.35in}

\textbf{Question 3.2}\\[-0.15em]
``Not every ticket holder was seated before the show began.'' Translate into a clear standard-form categorical proposition. State the subject and predicate you chose.

\answerbox{ANSWER LABEL: Part 3 Q2}{2.35in}

\newpage

\section*{Part 4: Distribution and Clarity}

\textbf{Question 4.1}\\[-0.15em]
For the standard-form proposition you wrote in Part 3 Q2, which term is distributed and which is undistributed? Briefly explain.

\answerbox{ANSWER LABEL: Part 4 Q1}{2.15in}

\textbf{Question 4.2}\\[-0.15em]
Read the exchange. Explain what quantity Person A left unclear and how that affects whether Person B's reply refutes the claim.

\vspace{0.2em}

\noindent\fbox{%
\begin{minipage}{\dimexpr\textwidth-2\fboxsep-2\fboxrule}
\vspace{0.35em}
Person A: ``Coaches are unfair to substitutes.'' Person B: ``That is false. My coach gave me extra practice time last week.''
\vspace{0.35em}
\end{minipage}
}

\answerbox{ANSWER LABEL: Part 4 Q2}{2.45in}

\newpage

\section*{Part 5: Review}

\textbf{Question 5.1}\\[-0.15em]
``The software update fixed every bug reported last month, so the app must be secure against all future attacks.'' Use the four-step test.

\answerbox{ANSWER LABEL: Part 5 Q1}{2.35in}

\textbf{Question 5.2}\\[-0.15em]
``You have a right to appeal the grade, but that does not mean your answer is right.'' Which word is used in two different senses? State both meanings.

\answerbox{ANSWER LABEL: Part 5 Q2}{1.65in}

\end{document}