\documentclass[12pt]{article}
\usepackage[margin=0.6in,top=0.85in,bottom=0.55in]{geometry}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{lastpage}
\usepackage[hidelinks]{hyperref}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.25em}
\setlength{\headheight}{26pt}
\titleformat{\section}{\large\bfseries\scshape}{}{0pt}{}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[C]{\footnotesize Student Name: \hspace{2.3in} \quad Assignment ID: U1L8LL \quad Page \thepage\ of \pageref{LastPage}}
\renewcommand{\headrulewidth}{0.5pt}

\newcommand{\answerbox}[2]{%
\vspace{0.15em}
\noindent\textbf{#1}\par
\vspace{0.05em}
\noindent\fbox{%
\begin{minipage}[t][#2]{\dimexpr\textwidth-2\fboxsep-2\fboxrule}
\rule{\textwidth}{0pt}
\vspace{#2}
\end{minipage}
}\par
\vspace{0.25em}
}

\begin{document}

\begin{center}
{\LARGE\bfseries Week 8 Logic Lab}\par\vspace{0.05em}
{\large\scshape Equivocation and the Ambiguous Middle}\par\vspace{0.1em}
\rule{0.78\textwidth}{0.5pt}\par\vspace{0.15em}
\end{center}

\noindent\textbf{Purpose:} Apply Week 8 skills to new examples. Do not copy examples from the reading handout.

\vspace{0.3em}

\section*{Part 1: Spot the Shift}

\textbf{Question 1.1}\\[-0.15em]
``All bats sleep upside down in caves. The coach ordered new bats. Therefore the coach ordered new animals that sleep upside down in caves.'' Identify the shifting term and state both meanings.

\answerbox{ANSWER LABEL: Part 1 Q1}{2.15in}

\textbf{Question 1.2}\\[-0.15em]
``All fairs are outdoor festivals with vendors. The referee's call was fair. Therefore the referee's call was an outdoor festival with vendors.'' Identify the shifting term and state both meanings.

\answerbox{ANSWER LABEL: Part 1 Q2}{2.15in}

\newpage

\section*{Part 2: Ambiguous Middle}

\textbf{Question 2.1}\\[-0.15em]
``All planes are objects that can fly under their own power. The geometry worksheet has several planes. Therefore the geometry worksheet has several objects that can fly under their own power.'' Explain why the middle term fails to connect the premises.

\answerbox{ANSWER LABEL: Part 2 Q1}{2.45in}

\newpage

\section*{Part 3: Fix and Retest}

\textbf{Question 3.1}\\[-0.15em]
``All people who are present are people who should vote now. The gift is present. Therefore the gift should vote now.'' Rewrite the argument with fixed meanings and say whether the original conclusion still follows.

\answerbox{ANSWER LABEL: Part 3 Q1}{2.85in}

\newpage

\section*{Part 4: Argument in a Paragraph}

\textbf{Question 4.1}\\[-0.15em]
Read the paragraph. Identify the shifting term, both meanings, and explain why the main conclusion does not follow.

\vspace{0.2em}

\noindent\fbox{%
\begin{minipage}{\dimexpr\textwidth-2\fboxsep-2\fboxrule}
\vspace{0.35em}
After the assembly, the principal praised the sound system and said the debate club needed a sound argument for the budget. One student answered that their argument was sound because the microphones were sound during the rehearsal. The janitor asked people to recycle cups. The student finished: ``If the argument is sound, the board should fund the trip. Our argument is sound. Therefore the board should fund the trip.''
\vspace{0.35em}
\end{minipage}
}

\answerbox{ANSWER LABEL: Part 4 Q1}{2.55in}

\newpage

\section*{Part 5: Review}

\textbf{Question 5.1}\\[-0.15em]
``Anyone who questions the spirit-week schedule is against school pride. You questioned the schedule. Therefore you are against school pride.'' Perform a short fallacy autopsy: conclusion, apparent proof, and defect.

\answerbox{ANSWER LABEL: Part 5 Q1}{2.15in}

\textbf{Question 5.2}\\[-0.15em]
``All songbirds are animals that can fly long distances over open water. All albatrosses are songbirds. Therefore all albatrosses are animals that can fly long distances over open water.'' Apply the form test, then name the main fact-test problem.

\answerbox{ANSWER LABEL: Part 5 Q2}{1.85in}

\end{document}
