\documentclass[12pt]{article}
\usepackage[margin=0.6in,top=0.85in,bottom=0.55in]{geometry}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{lastpage}
\usepackage[hidelinks]{hyperref}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.25em}
\setlength{\headheight}{26pt}
\titleformat{\section}{\large\bfseries\scshape}{}{0pt}{}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[C]{\footnotesize Student Name: \hspace{2.3in} \quad Assignment ID: U1L6LE \quad Page \thepage\ of \pageref{LastPage}}
\renewcommand{\headrulewidth}{0.5pt}

\newcommand{\answerbox}[2]{%
\vspace{0.12em}
\noindent\textbf{#1}\par
\vspace{0.04em}
\noindent\fbox{%
\begin{minipage}[t][#2]{\dimexpr\textwidth-2\fboxsep-2\fboxrule}
\rule{\textwidth}{0pt}
\vspace{#2}
\end{minipage}}
\par\vspace{0.22em}}

\begin{document}

\begin{center}
{\LARGE\bfseries Week 6 Lit Example Worksheet}\par\vspace{0.05em}
{\large\scshape Julius Caesar: Valid Form, Unproved Premise}\par\vspace{0.12em}
\rule{0.78\textwidth}{0.5pt}
\end{center}

\textbf{Purpose:} Apply Week 6's Whately method to Julius Caesar. Run the form test and the fact test separately before diagnosing soundness.

\textbf{Directions:} Use the Lit Example Reader. Do not collapse validity, truth, and persuasion into one answer.

\section*{Part 1: Form Test}

\textbf{Question 1.1}\\[-0.15em]
Reconstruct Brutus's argument in this form: All M are P; All S are M; therefore All S are P. Name M, S, and P.

\answerbox{ANSWER LABEL: Part 1 Q1}{2.45in}

\textbf{Question 1.2}\\[-0.15em]
Apply the form test only. If Brutus's two premises were true, would the conclusion follow? Explain.

\answerbox{ANSWER LABEL: Part 1 Q2}{2.1in}

\newpage

\section*{Part 2: Fact Test}

\textbf{Question 2.1}\\[-0.15em]
Which premise in Brutus's argument most needs factual proof? Explain why it is the pressure-point premise.

\answerbox{ANSWER LABEL: Part 2 Q1}{2.35in}

\textbf{Question 2.2}\\[-0.15em]
What evidence would Brutus need in order to make that premise strong enough for a careful listener?

\answerbox{ANSWER LABEL: Part 2 Q2}{2.35in}

\newpage

\section*{Part 3: Antony's Evidence}

\textbf{Question 3.1}\\[-0.15em]
List Antony's three main pieces of evidence against Brutus's ambition premise.

\answerbox{ANSWER LABEL: Part 3 Q1}{2.15in}

\textbf{Question 3.2}\\[-0.15em]
Does Antony prove that Caesar was not ambitious, or does he mainly make Brutus's premise doubtful? Explain the difference.

\answerbox{ANSWER LABEL: Part 3 Q2}{2.55in}

\newpage

\section*{Part 4: Final Diagnosis}

\textbf{Question 4.1}\\[-0.15em]
Diagnose Brutus's argument as valid, invalid, sound, unsound, or not yet proved. You may use more than one label if you explain the difference.

\answerbox{ANSWER LABEL: Part 4 Q1}{2.55in}

\textbf{Question 4.2}\\[-0.15em]
In one paragraph, explain why ``valid'' does not mean ``true'' using Brutus and Antony as your example.

\answerbox{ANSWER LABEL: Part 4 Q2}{2.45in}

\end{document}
