\documentclass[12pt]{article}
\usepackage[margin=0.6in,top=0.85in,bottom=0.55in]{geometry}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{lastpage}
\usepackage[hidelinks]{hyperref}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.25em}
\setlength{\headheight}{26pt}
\titleformat{\section}{\large\bfseries\scshape}{}{0pt}{}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[C]{\footnotesize Student Name: \hspace{2.3in} \quad Assignment ID: U1L11LL \quad Page \thepage\ of \pageref{LastPage}}
\renewcommand{\headrulewidth}{0.5pt}

\newcommand{\answerbox}[2]{%
\vspace{0.15em}
\noindent\textbf{#1}\par
\vspace{0.05em}
\noindent\fbox{%
\begin{minipage}[t][#2]{\dimexpr\textwidth-2\fboxsep-2\fboxrule}
\rule{\textwidth}{0pt}
\vspace{#2}
\end{minipage}
}\par
\vspace{0.25em}
}

\begin{document}

\begin{center}
{\LARGE\bfseries Week 11 Logic Lab}\par\vspace{0.05em}
{\large\scshape Analogy and Relevant Similarity}\par\vspace{0.1em}
\rule{0.78\textwidth}{0.5pt}\par\vspace{0.15em}
\end{center}

\noindent\textbf{Purpose:} Apply Week 11 skills to new examples. Do not copy examples from the reading handout.

\vspace{0.3em}

\section*{Part 1: Source, Target, and Claim}

\textbf{Question 1.1}\\[-0.15em]
``Changing the lunch schedule is like changing the traffic pattern outside school: if people do not get clear signs ahead of time, the first week will be chaos. Therefore the school should publish the new lunch schedule before the change begins.'' Identify the source case, target case, and conclusion.

\answerbox{ANSWER LABEL: Part 1 Q1}{2.35in}

\textbf{Question 1.2}\\[-0.15em]
``A research paper is like a building: without a foundation, everything above it is shaky. Therefore my draft needs stronger sources before I revise the introduction.'' Identify the source case, target case, and conclusion.

\answerbox{ANSWER LABEL: Part 1 Q2}{2.35in}

\newpage

\section*{Part 2: Relevant Similarity and Disanalogy}

\textbf{Question 2.1}\\[-0.15em]
``A team captain is like a point guard: both have to notice the whole field of play, not only their own statistics. Therefore captain selection should consider communication, not only scoring.'' State the relevant similarity and one important disanalogy.

\answerbox{ANSWER LABEL: Part 2 Q1}{2.5in}

\textbf{Question 2.2}\\[-0.15em]
``A school dress code is like a uniform for a job: it teaches professionalism, so every student should receive detention for any violation.'' State the similarity being used and one disanalogy that limits the conclusion.

\answerbox{ANSWER LABEL: Part 2 Q2}{2.55in}

\newpage

\section*{Part 3: Does the Analogy Prove Too Much?}

\textbf{Question 3.1}\\[-0.15em]
``Phones in class are like open bags of candy during practice: even if one person can ignore them, most people will be distracted. Therefore the class should have a phone plan during quizzes.'' Decide whether the analogy proves the whole claim, supports a narrower claim, or merely decorates the argument. Explain.

\answerbox{ANSWER LABEL: Part 3 Q1}{2.75in}

\textbf{Question 3.2}\\[-0.15em]
``Choosing a college is like choosing a winter coat: the cheapest option is always the smartest choice because both decisions are mostly about price.'' Decide whether the analogy proves the whole claim, supports a narrower claim, or merely decorates the argument. Explain.

\answerbox{ANSWER LABEL: Part 3 Q2}{2.75in}

\newpage

\section*{Part 4: Argument in a Paragraph}

\textbf{Question 4.1}\\[-0.15em]
Read the paragraph. Apply the analogy test: identify the conclusion, source and target cases, relevant similarity, important disanalogy, and best judgment.

\vspace{0.2em}

\noindent\fbox{%
\begin{minipage}{\dimexpr\textwidth-2\fboxsep-2\fboxrule}
\vspace{0.35em}
At the student council meeting, Lena argued that the school should start the new tutoring program with ninth graders only. ``A garden bed needs one section planted first,'' she said. ``If the first section grows well, you learn what soil, water, and spacing work before planting the whole field. Ninth grade has the most new students and the clearest need for study routines. Start there, measure results for a quarter, and then expand.'' Another student objected that people are not plants and that older students also need help.
\vspace{0.35em}
\end{minipage}
}

\answerbox{ANSWER LABEL: Part 4 Q1}{3.0in}

\newpage

\section*{Part 5: Review}

\textbf{Question 5.1}\\[-0.15em]
``The committee proved that the mural would make the hallway brighter and more interesting. Therefore the committee proved the mural is the best use of the entire arts budget.'' Name the earlier-week defect and explain it briefly.

\answerbox{ANSWER LABEL: Part 5 Q1}{2.0in}

\textbf{Question 5.2}\\[-0.15em]
``Only reliable sources correct their errors publicly. This website corrected an error publicly. Therefore this website is reliable.'' Identify the structure problem and say whether the conclusion follows.

\answerbox{ANSWER LABEL: Part 5 Q2}{2.0in}

\end{document}
