\documentclass[12pt]{article}
\usepackage[margin=0.6in,top=1.15in,bottom=0.55in]{geometry}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{../../latex/grader-worksheet}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.25em}
\titleformat{\section}{\large\bfseries\scshape}{}{0pt}{}

\GraderSetup{assignment-id=U1L17LL,template-revision=1}

\begin{document}

\begin{center}
{\LARGE\bfseries Week 17 Logic Lab}\par\vspace{0.05em}
{\large\scshape Self-Deception and Private Justification}\par\vspace{0.1em}
\rule{0.78\textwidth}{0.5pt}\par\vspace{0.15em}
\end{center}

\noindent\textbf{Purpose:} Apply a multi-tool Whately autopsy to fresh cases of self-justification: name desire, conclusion, hidden assumption, flaw, and a repaired narrower claim.

\vspace{0.3em}

\section*{Part 1: Desire and Conclusion}

\textbf{Question 1.1}\\[-0.15em]
After missing two practices, a starter tells himself, ``The coach is unfair, so I deserve to start anyway.'' Name the desire or feared loss and the conclusion he wants.

\GraderAnswerBox{Part 1 Q1}{2.35in}

\textbf{Question 1.2}\\[-0.15em]
A student who has not opened the novel says, ``I work better under pressure, so waiting until tonight is actually smart planning.'' Name the desire and the conclusion.

\GraderAnswerBox{Part 1 Q2}{2.35in}

\newpage

\section*{Part 2: Hidden Assumption and Tool}

\textbf{Question 2.1}\\[-0.15em]
``I already put hours into this group project, therefore my method is the best method.'' Surface the hidden assumption and name one Whately tool that exposes the flaw.

\GraderAnswerBox{Part 2 Q1}{2.55in}

\textbf{Question 2.2}\\[-0.15em]
``My friend said the shortcut is safe, and my friend always has my back, so the shortcut is safe.'' Surface the weak move and name the prior-week credibility or proof tool that tests it.

\GraderAnswerBox{Part 2 Q2}{2.45in}

\newpage

\section*{Part 3: Private Argument and Public Cover}

\textbf{Question 3.1}\\[-0.15em]
Privately, a club officer wants the title for college applications. Publicly, the officer says, ``I am running only because the club needs continuity.'' What is the private argument, what is the public cover, and what independent support would the public cover need?

\GraderAnswerBox{Part 3 Q1}{2.55in}

\textbf{Question 3.2}\\[-0.15em]
A driver who was texting says, ``Anyone would have looked down for a second; the real problem is these sudden stoplights.'' Identify the rationalization and a repaired claim that stays closer to the facts.

\GraderAnswerBox{Part 3 Q2}{2.55in}

\newpage

\section*{Part 4: Full Self-Deception Autopsy}

\textbf{Question 4.1}\\[-0.15em]
Read the paragraph. Complete a self-deception autopsy: desire, conclusion, stated reasons, hidden assumption, one exposing tool, what still needs judgment or evidence, and a repaired narrower claim.

\vspace{0.2em}

\noindent\fbox{%
\begin{minipage}{\dimexpr\textwidth-2\fboxsep-2\fboxrule}
\vspace{0.35em}
Jordan wants the lead in the spring play. After a shaky audition, Jordan thinks: ``The director likes people who look confident. I looked nervous, but that is only because I care more than the others. Caring that much means I should get the part. If I do not get it, the process was biased. Anyway, everyone says hard workers are rewarded, and no one works harder than I do in my head.''
\vspace{0.35em}
\end{minipage}
}

\GraderAnswerBox{Part 4 Q1}{3.2in}

\newpage

\section*{Part 5: Review}

\textbf{Question 5.1}\\[-0.15em]
A campaign video shows slow music, a torn flag, and the line ``Trust me---I am one of you,'' then asks voters to reject a budget report they have not read. Use a prior-week rhetoric tool: what is the rhetorical force, and what remains unproved?

\GraderAnswerBox{Part 5 Q1}{2.2in}

\textbf{Question 5.2}\\[-0.15em]
Two students argue whether a punishment was ``fair.'' After they agree fair means ``same rule applied the same way,'' they still disagree about the facts of the case. Use a prior-week dispute tool: classify the remaining disagreement.

\GraderAnswerBox{Part 5 Q2}{2.05in}

\end{document}
