\documentclass[12pt]{article}
\usepackage[margin=0.6in,top=0.85in,bottom=0.55in]{geometry}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{lastpage}
\usepackage[hidelinks]{hyperref}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.25em}
\setlength{\headheight}{26pt}

\titleformat{\section}{\large\bfseries\scshape}{}{0pt}{}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[C]{%
\footnotesize
Student Name: \hspace{2.3in} \quad Assignment ID: U1L1LL \quad Page \thepage\ of \pageref{LastPage}
}
\renewcommand{\headrulewidth}{0.5pt}
\renewcommand{\footrulewidth}{0pt}

\newcommand{\answerbox}[2]{% #1 = label, #2 = height
\vspace{0.15em}
\noindent\textbf{#1}\par
\vspace{0.05em}
\noindent\fbox{%
\begin{minipage}[t][#2]{\dimexpr\textwidth-2\fboxsep-2\fboxrule}
\rule{\textwidth}{0pt}
\vspace{#2}
\end{minipage}
}\par
\vspace{0.25em}
}

\begin{document}

\begin{center}
{\LARGE\bfseries Week 1 Logic Lab}\par\vspace{0.05em}
{\large\scshape Parsing Arguments in Fresh Cases}\par\vspace{0.1em}
\rule{0.78\textwidth}{0.5pt}\par\vspace{0.15em}
\end{center}

\noindent\textbf{Purpose:} Use Whately's four-step test on \textbf{new} examples. For each argument below, work with: \textbf{Conclusion} (what is being claimed), \textbf{Stated reason} (what support is actually given), \textbf{Hidden assumption} (what unstated idea must be true for the reason to prove the conclusion), and \textbf{Follows} (does the conclusion actually follow?). Do not copy examples from the reading handout; reason about the sentences given here.

\vspace{0.3em}

\section*{Part 1: Name the Claim and the Reason}

\textbf{Part 1 Q1:} ``Our team has won its last three games, so we will definitely win the championship.'' State the \textbf{conclusion} and the \textbf{stated reason} in your own words.

\answerbox{Part 1 Q1 ANSWER BOX}{1.65in}

\textbf{Part 1 Q2:} ``She apologized in a sincere tone, so she must truly regret what she did.'' State the \textbf{conclusion} and the \textbf{stated reason} in your own words.

\answerbox{Part 1 Q2 ANSWER BOX}{1.65in}

\newpage

\section*{Part 2: Full Four-Step Test}

\textbf{Part 2 Q1:} ``This study app has been downloaded five million times, so it must be the best tool for learning chemistry.'' Identify the conclusion, stated reason, hidden assumption, and whether the conclusion follows.

\answerbox{Part 2 Q1 ANSWER BOX}{2.5in}

\textbf{Part 2 Q2:} ``The weather report predicts rain on Saturday, so we should call off Friday night's outdoor concert.'' Identify the conclusion, stated reason, hidden assumption, and whether the conclusion follows.

\answerbox{Part 2 Q2 ANSWER BOX}{2.5in}

\newpage

\section*{Part 3: Trickier Everyday Arguments}

\textbf{Part 3 Q1:} ``Every member of the student council voted for this proposal, so the proposal must be fair.'' Identify the conclusion, stated reason, hidden assumption, and whether the conclusion follows.

\answerbox{Part 3 Q1 ANSWER BOX}{2.55in}

\textbf{Part 3 Q2:} ``No one in this debate club has read more sources than Jordan, so Jordan's conclusion must be correct.'' Identify the conclusion, stated reason, hidden assumption, and whether the conclusion follows.

\answerbox{Part 3 Q2 ANSWER BOX}{2.55in}

\newpage

\section*{Part 4: Find the Argument in a Paragraph}

\textbf{Part 4 Q1:} Read the paragraph below. It mixes scene-setting details with one main argument. Ignore the distractors. Identify the \textbf{conclusion}, \textbf{stated reason}, \textbf{hidden assumption}, and whether the conclusion \textbf{follows}. Label your answer clearly.

\vspace{0.2em}

\noindent\fbox{%
\begin{minipage}{\dimexpr\textwidth-2\fboxsep-2\fboxrule}
\vspace{0.35em}
The city council met in a crowded hall while protesters chanted outside and a local reporter live-streamed the first hour. Council member Ortiz reminded everyone that her brother once missed work because of a bus delay. After the budget officer reviewed last year's spending charts, the council voted to expand late-night bus service. Supporters said that workers on evening shifts often cannot get home safely and that ridership on the pilot route rose after the trial began. A few online commenters joked that the city should buy everyone scooters instead. The council's decision, announced just before midnight, was that late-night bus service should be widened across the east side.
\vspace{0.35em}
\end{minipage}
}

\answerbox{Part 4 Q1 ANSWER BOX}{2.85in}

\end{document}