\documentclass[12pt]{article}
\usepackage[margin=0.6in,top=0.85in,bottom=0.55in]{geometry}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{array}
\usepackage{lastpage}
\usepackage[hidelinks]{hyperref}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.22em}
\setlength{\headheight}{26pt}
\titleformat{\section}{\large\bfseries\scshape}{}{0pt}{}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[C]{\footnotesize Student Name: \hspace{2.0in} \quad Assignment ID: U1F1LD \quad Page \thepage\ of \pageref{LastPage}}
\renewcommand{\headrulewidth}{0.5pt}
\renewcommand{\footrulewidth}{0pt}

\newcommand{\answerbox}[2]{%
\vspace{0.12em}\noindent\textbf{#1}\par\vspace{0.04em}
\noindent\fbox{\begin{minipage}[t][#2]{\dimexpr\textwidth-2\fboxsep-2\fboxrule}\rule{\textwidth}{0pt}\vspace{#2}\end{minipage}}\par\vspace{0.22em}}

\newcommand{\cluebox}[1]{%
\noindent\fbox{\begin{minipage}{\dimexpr\textwidth-2\fboxsep-2\fboxrule}\vspace{0.3em}#1\vspace{0.3em}\end{minipage}}}

\begin{document}

\begin{center}
{\LARGE\bfseries Logic Dungeon I}\par\vspace{0.04em}
{\large\scshape The Hall of Inscriptions}\par\vspace{0.08em}
\rule{0.78\textwidth}{0.5pt}\par\vspace{0.12em}
\end{center}

\textbf{Purpose:} Use the logic tools from Weeks 1--3 to decide which door is best supported.

\section*{The Three Doors}

Twenty adventurers enter the first underground passage toward \textit{Castrum Malae Ratiocinationis}. Their lamps are failing. To continue, they must find the passage most likely to rise toward natural daylight.

Three doors face them:

\begin{itemize}[leftmargin=1.5em,itemsep=0.1em]
\item \textbf{Laurel Door} --- carved with leaves; a brass lantern burns beside it.
\item \textbf{Echo Door} --- hung with a bell; its first chamber is dry and uncracked.
\item \textbf{Slate Door} --- marked with a square; pale sand lies beneath its frame.
\end{itemize}

Every station has two jobs. First, solve the logic problem. Second, decide what the expedition may record about the doors. A clue may be true yet useless. A bad argument may contain a useful fact. A later clue may make an earlier observation important.

\cluebox{\textbf{Rule of evidence:} Use only the supplied evidence. Record what it establishes, what it does not establish, and whether it helps distinguish among the doors. The goal is the \emph{best-supported next step}, not a guarantee of safety.}

\vspace{0.3em}
\textbf{Tools available:} conclusion, stated reason, hidden assumption, follow-test; stable terms; subject and predicate; quality and quantity; A/E/I/O; scope; limits of logic.

\vfill
\textit{The oldest inscription in the hall reads: ``The obvious clue is often only the loudest.''}

\newpage

\section*{Part 1: The Laurel Chorus --- Danger Station}

Above the Laurel Door, one hundred small bronze hands are fixed to the wall. When the lantern warms them, they clap. An inscription reads:

\cluebox{``Travelers have applauded the Laurel passage for a hundred years. Therefore Laurel is the wisest road to daylight.''}

\textbf{Part 1 Q1:} Identify the conclusion, stated reason, and hidden assumption. Decide whether the conclusion follows.

\answerbox{Part 1 Q1 ANSWER BOX}{2.25in}

\textbf{Part 1 Q2:} What may the expedition record about Laurel after solving Q1? State what the applause establishes, what it does not establish, and whether this clue helps choose the door.

\answerbox{Part 1 Q2 ANSWER BOX}{2.05in}

\newpage

\section*{Part 2: The Two-Voiced Guide --- Danger Station}

A stone guide beside the Echo Door announces:

\cluebox{``The Echo passage is sound; masons found no cracks in its first chamber. Every sound choice deserves trust. Therefore Echo is the sound road to daylight.''}

\textbf{Part 2 Q1:} Identify the word that changes meaning. Explain both meanings, rewrite the argument with one stable meaning, and decide what follows.

\answerbox{Part 2 Q1 ANSWER BOX}{2.45in}

\textbf{Part 2 Q2:} What may the expedition record about Echo? Separate the useful fact hidden inside the bad argument from what remains unproved. Does it help with safety, direction, both, or neither?

\answerbox{Part 2 Q2 ANSWER BOX}{1.85in}

\newpage

\section*{Part 3: The Three-Chamber Field Ledger}

A scout sampled only the first chamber behind each door. The ledger is \textbf{not} a complete census of any passage.

\cluebox{
\begin{tabular}{>{\bfseries}p{0.18\textwidth}p{0.74\textwidth}}
Laurel & Two ash moths circling the brass lantern; both winged.\\
Echo & Two cave beetles beside the dry wall; one winged and one not winged.\\
Slate & Two glass ants crossing the pale sand; both winged and moving in a single line beneath the square mark.\\
\end{tabular}}

The scout writes:

\begin{enumerate}[label=\Alph*.,leftmargin=2em,itemsep=0.1em]
\item All observed Laurel ash moths are winged creatures.
\item No observed Echo cave beetles are winged creatures.
\item Some observed Slate glass ants are winged creatures.
\item Most creatures in the Hall are winged creatures.
\end{enumerate}

\textbf{Part 3 Q1:} For A, B, and C, identify A/E/I/O form, quality, and quantity. For C, identify subject and predicate. Which claim is contradicted by the ledger?

\answerbox{Part 3 Q1 ANSWER BOX}{2.2in}

\textbf{Part 3 Q2:} Which claim reaches farthest beyond the sample and is least useful for choosing a door? Explain. Then write one precise route observation the expedition may preserve for later.

\answerbox{Part 3 Q2 ANSWER BOX}{1.85in}

\newpage

\section*{Part 4: The Naturalist's Key}

Farther along the hall, the expedition finds a recent field card stamped by the Academy naturalist:

\cluebox{
\begin{enumerate}[label=\arabic*.,leftmargin=1.7em,itemsep=0.12em]
\item Ash moths circle any warm lamp, whether or not natural daylight is nearby.
\item Cave beetles live in both upper and lower tunnels.
\item All glass-ant trail lines carrying pale sand lead toward openings reached by natural daylight.
\item Some glass ants wander without forming a trail line.
\end{enumerate}}

\textbf{Part 4 Q1:} Put Statement 3 into clear A form. Identify its subject, predicate, quality, and quantity. Explain why Statement 4 does not contradict it.

\answerbox{Part 4 Q1 ANSWER BOX}{2.15in}

\textbf{Part 4 Q2:} Combine the key with the earlier ledger. Which observations are now useful, useless, or distracting for the search for daylight? Explain the strongest route inference without changing \emph{some} into \emph{all}.

\answerbox{Part 4 Q2 ANSWER BOX}{2.15in}

\newpage

\section*{Part 5: The Compass and the Old Map}

Two final objects lie on a plinth:

\cluebox{\textbf{The compass:} Its needle points toward Laurel. A small plate beneath it says, ``Iron hinge directly behind Laurel Door.''

\textbf{The mapmaker's oath:} ``I copied every line carefully from an older map. Therefore this map gives the true condition of all three passages today.'' The old map has no date or maker.}

\textbf{Part 5 Q1:} Use the four-step test on the mapmaker's oath. Then explain what logic can decide and what requires observation, testimony, or corroboration.

\answerbox{Part 5 Q1 ANSWER BOX}{2.35in}

\textbf{Part 5 Q2:} Evaluate the compass as route evidence. Is its direction false, true but irrelevant, or useful? Explain what the plate allows the expedition to infer.

\answerbox{Part 5 Q2 ANSWER BOX}{1.75in}

\newpage

\section*{Part 6: Expedition Evidence Chart}

Complete the chart before choosing. Use short phrases. Do not write ``safe'' unless the evidence establishes safety.

\renewcommand{\arraystretch}{1.5}
\begin{tabular}{|p{0.13\textwidth}|p{0.27\textwidth}|p{0.27\textwidth}|p{0.23\textwidth}|}
\hline
\textbf{Door} & \textbf{Established evidence} & \textbf{Still unproved} & \textbf{Help toward daylight?}\\ \hline
Laurel & & & \\[0.52in] \hline
Echo & & & \\[0.52in] \hline
Slate & & & \\[0.52in] \hline
\end{tabular}

\vspace{0.35em}
\textbf{Part 6 Q1:} Beneath the chart, identify the strongest clue, one useful-but-limited clue, and one distractor. Explain each classification briefly.

\answerbox{Part 6 Q1 ANSWER BOX}{1.75in}

\newpage

\section*{Part 7: The Door Decision}

\textbf{Part 7 Q1:} Which door is the best-supported next step toward daylight? Use at least three pieces of evidence from different parts. Explain why each rejected door has weaker directional support and state what remains unknown about your chosen passage.

\answerbox{Part 7 Q1 ANSWER BOX}{2.3in}

\newpage

\section*{Part 8: What Logic Has Not Given Us}

The company turns toward one door. Before anyone opens it, the expedition leader asks for one final act of precision.

\textbf{Part 8 Q1:} Name the next observation that would most improve the decision. Then complete: ``Logic helped us decide \rule{1.6in}{0.4pt}, but it could not by itself establish \rule{1.6in}{0.4pt}.''

\answerbox{Part 8 Q1 ANSWER BOX}{2.2in}

\textbf{Part 8 Q2:} A nervous adventurer says, ``Because Slate is best supported, Slate must be completely safe.'' Identify the conclusion, hidden assumption, and error. Repair the claim.

\answerbox{Part 8 Q2 ANSWER BOX}{2.2in}

\vfill
\begin{center}\textit{Best supported is not the same as guaranteed. The expedition proceeds with care.}\end{center}

\end{document}
