\documentclass[12pt]{article}
\usepackage[margin=0.6in,top=1.15in,bottom=0.55in]{geometry}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{../../latex/grader-worksheet}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.25em}

\titleformat{\section}{\large\bfseries\scshape}{}{0pt}{}

\GraderSetup{assignment-id=U1L2LL,template-revision=1}

\begin{document}

\begin{center}
{\LARGE\bfseries Week 2 Logic Lab}\par\vspace{0.05em}
{\large\scshape Terms, Ambiguity, and Equivocation}\par\vspace{0.1em}
\rule{0.78\textwidth}{0.5pt}\par\vspace{0.15em}
\end{center}

\noindent\textbf{Purpose:} Apply Week 2 skills to new examples. Do not copy examples from the reading handout.

\vspace{0.3em}

\section*{Part 1: Two Meanings in Context}

\textbf{Question 1.1}\\[-0.15em]
``You have a right to speak at the meeting, but that does not mean you are right about the policy.'' Which word is used in two different senses? State both meanings.

\GraderAnswerBox{Part 1 Q1}{1.55in}

\textbf{Question 1.2}\\[-0.15em]
``In a free country, admission to the public museum on holidays should be free.'' Which word is used in two different senses? State both meanings.

\GraderAnswerBox{Part 1 Q2}{1.65in}

\newpage

\section*{Part 2: Spot the Equivocation}

\textbf{Question 2.1}\\[-0.15em]
``What is light cannot be dark. Feathers are light. Therefore feathers cannot be dark.'' Identify the shifting term, both meanings, and explain why the conclusion does not follow.

\GraderAnswerBox{Part 2 Q1}{2.45in}

\textbf{Question 2.2}\\[-0.15em]
``All stars are balls of gas in space. The lead singer is a star. Therefore the lead singer is a ball of gas in space.'' Identify the shifting term, both meanings, and explain why the conclusion does not follow.

\GraderAnswerBox{Part 2 Q2}{2.45in}

\newpage

\section*{Part 3: Fix the Term}

\textbf{Question 3.1}\\[-0.15em]
``The end of a thing is its perfection. Death is the end of life. Therefore death is the perfection of life.'' Disambiguate the key term, then state whether the conclusion follows.

\GraderAnswerBox{Part 3 Q1}{2.55in}

\newpage

\section*{Part 4: Argument in a Paragraph}

\textbf{Question 4.1}\\[-0.15em]
Read the paragraph. Identify the equivocation and explain why the main inference is unreliable.

\vspace{0.2em}

\noindent\fbox{%
\begin{minipage}{\dimexpr\textwidth-2\fboxsep-2\fboxrule}
\vspace{0.35em}
After the student council election, Jordan said the loss made him feel like a nobody. The next day, a campaign flyer stated that nobody is perfect, so Jordan must be perfect in some respect. The yearbook editor praised the flyer for proving Jordan's excellence. Jordan said the flyer did not prove what the editor claimed.
\vspace{0.35em}
\end{minipage}
}

\GraderAnswerBox{Part 4 Q1}{2.75in}

\newpage

\section*{Part 5: Review — Week 1 Four-Step Test}

\textbf{Question 5.1}\\[-0.15em]
``The mayor has served in office longer than any other council member, so the mayor's new zoning plan must be lawful.'' Use the four-step test.

\GraderAnswerBox{Part 5 Q1}{2.35in}

\textbf{Question 5.2}\\[-0.15em]
``This clinic received the highest patient satisfaction scores, so its medical advice must be scientifically correct.'' Use the four-step test.

\GraderAnswerBox{Part 5 Q2}{2.35in}

\newpage

\textbf{Question 5.3}\\[-0.15em]
Read the paragraph. Parse the main argument using the four-step test.

\vspace{0.2em}

\noindent\fbox{%
\begin{minipage}{\dimexpr\textwidth-2\fboxsep-2\fboxrule}
\vspace{0.35em}
The hiring panel ate lunch in the courtyard while interns rearranged chairs. One member said her cousin dislikes early interviews. The panel chair noted that the finalist had answered every technical question correctly and that no other candidate had completed the same skills trial. A board observer posted a meme about trick questions online. The panel's official note said the finalist should be hired because proven test performance guarantees long-term success in the role.
\vspace{0.35em}
\end{minipage}
}

\GraderAnswerBox{Part 5 Q3}{2.85in}

\end{document}